Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-01-27 paper/main.tex
.

\todo[inline]{List a number of general challenges first, then refer
  back to them: very similar drugs are designed to target the same
  proteins, minor variations, leading to a kind of ``hidden''
  duplication of drugs in the training/testing set; some proteins act
  like hubs and interact with many drugs (making them easy and
  reliable predictors); shared indications of drugs are usually
  because they target the same proteins by design leading to some
  trivial predictions; some proteins are more ``valuable'' targets due
  to their disease involvement (such as cancer, meaning more drugs are
  developed for targeting those); }

>>>>

\todo[inline]{List a number of general challenges first, then refer
  back to them: very similar drugs are designed to target the same
  proteins, minor variations, leading to a kind of ``hidden''
  duplication of drugs in the training/testing set; some proteins act
  like hubs and interact with many drugs (making them easy and
  reliable predictors); shared indications of drugs are usually
  because they target the same proteins by design leading to some
  trivial predictions; some proteins are more ``valuable'' targets due
  to their disease involvement (such as cancer, meaning more drugs are
  developed for targeting those). If the aim is to find a drug for a
  given protein, the challenge is to develop a training (and
  evaluation) scheme that does not simply overfit to these biases.}
